Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-08 text/supp.tex
Add phylopic citations to supp

>>>>

\section{Additional acknowledgements}

Many of the silhouette images used in Figs~\ref{fig:nu-coefs}, \ref{fig:correlates} and \ref{fig:posteriors} were obtained from \texttt{phylopic.org} under Creative Commons licenses. We vectorized the salmon in Fig.~\ref{fig:nu-coefs} and Fig.~\ref{fig:correlates} ourselves. The bird in these figures was obtained from \texttt{phylopic.org} under a Creative Commons Attribution 3.0 Unported license with credit to Jean-Raphaël Guillaumin {[}photography{]} and T. Michael Keesey {[}vectorization{]}). The silhouettes in Fig.~\ref{fig:posteriors} were obtained from the following sources:

\LTcapwidth=\textwidth
\singlespacing
\begin{footnotesize}
\begin{longtable}{>{\RaggedRight}m{3.2cm}>{\RaggedRight}p{6.5cm}>{\RaggedRight}p{5.0cm}}
%\caption{Phylopic credits}\\
\toprule
\input{../analysis/phylopic.tex}
\label{tab:phylopic}
\end{longtable}
\end{footnotesize}
\onehalfspacing
